Manuscript title here

### 2024-10-15 manuscript.Rmd
la till kod för att kunna presentera tabell i dokument

---
title: "Manuscript title here"
author: "Your name here"
output:
  word_document: default
  html_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

```{r main, echo=FALSE}
source("main.R") ## This "imports" the main script file of your project and run any code in it
```

>>>>

---
title: "Manuscript title here"
author: "Your name here"
output:
  html_document: default
  word_document: default
bibliography: bibliography.bib
csl: vancouver.csl
---

@@

```{r main, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
source("main.R") ## This "imports" the main script file of your project and run any code in it
```
